Real Estate

### 2022-10-21 src/real_estate.Rmd

MSA_demo_data <- read_sheet("https://docs.google.com/spreadsheets/d/12do9sRCAcrIe0K-VcJWXNmmTm_jg5rKjZ0NeJPOm9Jw/edit#gid=0")
city_realEstate_ata <- read_sheet("https://docs.google.com/spreadsheets/d/12do9sRCAcrIe0K-VcJWXNmmTm_jg5rKjZ0NeJPOm9Jw/edit#gid=359643482")
```

>>>>

MSA_demo_data <- read_sheet("https://docs.google.com/spreadsheets/d/12do9sRCAcrIe0K-VcJWXNmmTm_jg5rKjZ0NeJPOm9Jw/edit#gid=0")
city_realEstate_data <- read_sheet("https://docs.google.com/spreadsheets/d/10n55Gt0rySN96OGTQ2_8PzeTcX66n26sOlZBiuiAeBU/edit#gid=808954990")
```
